### 2018-07-31 README.Rmd
minimal examples

By default, this will install the database into a hidden `.taxald` folder in your home directory (`~/.taxald`).  You can control this by passing the path to `create_taxadb()` or setting the environmental variable `TAXALD_HOME` to a different location.

@@

First, let's get a nice big species list, say, all the birds (known to the Catalogue of Life):

```{r}
tic()
df <- descendents(name = "Aves", rank = "class", authority="col")
toc()
```

@@

```{r}
length(df$name)
```

In general, this species list could have come from anywhere (i.e. some particular research project) and not from a single authority.

@@

```{r}
tic()
hierarchy(df$name)
toc()
```

>>>>

The default behavior installs only the ITIS database using the hierachy schema.  While this should be sufficient for getting started on basic tasks like looking up classification or translating between IDs and scientific names, users will want to install additional authorities and schemas for advanced use. See the `authorities` vignette for details.  By default, `taxald` will install the database into a hidden `.taxald` folder in your home directory (`~/.taxald`).  You can control this by passing the path to `create_taxadb()` or setting the environmental variable `TAXALD_HOME` to a different location.

@@

First, let's get a nice big species list, say, all the birds (known to ITIS):

```{r}
tic()
df <- descendants(name = "Aves", rank = "class")
toc()
```

@@

```{r}
length(df$species)
```

Generally, we have a species list could have come from some particular research project, and the names may not match those of any one particular authority.

```{r}
tic()
ids(df$species)
toc()
```

@@

```{r}
tic()
classification(df$species)
toc()
```
